Investigating the Underprovision of Public Goods: Does Segregation Matter?

### 2020-05-07 final_draft_extension_fs.Rmd
edits to text

nrow(fin_imp_pop_over_baqir)

@@

fit_over_baqir_1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

@@

@@

fit_under_baqir_1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

@@

pop_data_over_baqir <- tibble(
  log_pop = complete(imp_fs_pop_overbaqir,1)$logpop,
  Analysis = "Imputed, pop. > 25k"
)

pop_data_under_baqir <- tibble(
  log_pop = complete(imp_fs_pop_under_baqir, 1)$logpop,
  Analysis = "Imputed, pop. < 25k"
)

pop_data_imp_fs <- tibble(
  log_pop = complete(imp_fs, 1)$logpop,
  Analysis = "Imputed, Whole Sample"
)

pop_hist_data %>%
  ggplot() +
  geom_histogram(aes(x = log_pop, fill = Analysis)) +
  geom_vline(aes(xintercept = median_log_pop), color = "red") +
  facet_wrap(~Analysis) +
  coord_cartesian(xlim = c(0,15)) +
  ggtitle("Histograms of Log Populaiton of City Observations Included in the\nVarious Regression Analyses") +
  labs(caption = "This figure makes clear the differences in city size (in terms of population) among the different analyses.\n It is clear that the listwise deletion of observations with missing values resulted in a sample that almost entirely\nconsisted of larger cities in Trounstine (2016). The distribution of city population in Trounstine (2016)\nmore closely resembles the distribution of the original sample with a greater than 25,000 population\ncutoff imposed than the original sample. The red lines indicate the median log population in each sample.") +
  ylab("Count") +
  xlab("Log Population") +
  theme_bw() +
  theme(plot.caption = element_text(hjust = 0),
        strip.text.x = element_text(size = 8))

@@

nrow(fin_imp_top_1)

@@

fit_fs_pop_top_1 <- with(imp_fs_pop_top_1, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

@@

```{r}
fin_seg %>%
  ggplot(aes(x = logpop)) +
  geom_histogram() +
  geom_vline(aes(xintercept = log(25000)))

log(25000)
```

@@

nrow(fin_imp_bottom_60)

@@

fit_imp_bottom_60 <- with(imp_bottom_60, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

@@

@@

fit_imp_50k <- with(imp_50k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

@@

fit_imp_250k <- with(imp_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp + logpop | factor(geo_id2) |0| geo_id2))

@@

```{r 500k}

@@

@@

@@

@@

@@

imp_felm1_sum[1,2]
imp_under_baqir_1_sum
imp_over_baqir_1_sum
#coef(felm1)[1]
imp_fs_pop_top_1_sum

@@

model_coeff <- tibble(
  variable = c("White/Non-White Seg. Index", "Diversity", 
               "White/Non-White Seg. Index", "Diversity", 
               #"White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity"),
  estimate = c(imp_under_baqir_1_sum[1,2], imp_under_baqir_1_sum[2,2],
               imp_felm1_sum[1,2], imp_felm1_sum[2,2],
               #coef(felm1)[1], coef(felm1)[2],
               imp_over_baqir_1_sum[1,2], imp_over_baqir_1_sum[2,2],
               imp_fs_pop_top_1_sum[1,2], imp_fs_pop_top_1_sum[2,2]),
  std_error = c(imp_under_baqir_1_sum[1,3], imp_under_baqir_1_sum[2,3],
                imp_felm1_sum[1,3], imp_felm1_sum[2,3],
                #summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2],
                imp_over_baqir_1_sum[1,3], imp_over_baqir_1_sum[2,3],
                imp_fs_pop_top_1_sum[1,3], imp_fs_pop_top_1_sum[2,3]),
  model = c(1, 1, 
            2, 2,
            #3, 3,
            3, 3,
            5, 5)
)

@@

>>>>

nrow(fin_imp_pop_over_baqir)
median(fin_imp_pop_over_baqir$logpop)

@@

fit_over_baqir_1 <- with(imp_fs_pop_overbaqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

@@

nrow(fin_imp_pop_under_baqir)
median(fin_imp_pop_under_baqir$logpop)

@@

fit_under_baqir_1 <- with(imp_fs_pop_under_baqir, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

@@

@@

nrow(fin_imp_top_1)
median(fin_imp_top_1$logpop)
# generate a blank run to get the method matrix

@@

fit_fs_pop_top_1 <- with(imp_fs_pop_top_1, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

@@

@@

nrow(fin_imp_bottom_60)
median(fin_imp_bottom_60$logpop)

@@

fit_imp_bottom_60 <- with(imp_bottom_60, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

@@

```{r 60-80}

quantile(fin_seg$logpop, c(.60, .8), na.rm = T)

fin_imp_60_80 <- fin_imp %>%
  filter(logpop > quantile(fin_seg$logpop, c(.60), na.rm = T) & logpop < quantile(fin_seg$logpop, c(.80), na.rm = T))

nrow(fin_imp_60_80)
median(fin_imp_60_80$logpop)

ini <- mice(fin_imp_60_80, maxit = 0, print = FALSE)

imp_60_80 <- mice(fin_imp_60_80, method = meth, maxit = 5)

fit_imp_60_80 <- with(imp_60_80, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_60_80 <- pool(fit_imp_60_80)
imp_fs_60_80 <- summary(pool_fs_60_80)

```{r 80-100}

quantile(fin_seg$logpop, c(.60, .8), na.rm = T)

fin_imp_80_100 <- fin_imp %>%
  filter(logpop > quantile(fin_seg$logpop, c(.80), na.rm = T) & logpop < quantile(fin_seg$logpop, c(1), na.rm = T))

nrow(fin_imp_80_100)
median(fin_imp_80_100$logpop)

ini <- mice(fin_imp_80_100, maxit = 0, print = FALSE)

imp_80_100 <- mice(fin_imp_80_100, method = meth, maxit = 5)

fit_imp_80_100 <- with(imp_80_100, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_80_100 <- pool(fit_imp_80_100)
imp_fs_80_100 <- summary(pool_fs_80_100)

```{r 80-90}

quantile(fin_seg$logpop, c(.60, .8), na.rm = T)

fin_imp_80_90 <- fin_imp %>%
  filter(logpop > quantile(fin_seg$logpop, c(.80), na.rm = T) & logpop < quantile(fin_seg$logpop, c(.9), na.rm = T))

nrow(fin_imp_80_90)
median(fin_imp_80_90$logpop)

ini <- mice(fin_imp_80_90, maxit = 0, print = FALSE)

imp_80_90 <- mice(fin_imp_80_90, method = meth, maxit = 5)

fit_imp_80_90 <- with(imp_80_90, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_80_90 <- pool(fit_imp_80_90)
imp_fs_80_90 <- summary(pool_fs_80_90)

```{r 90-100}

fin_imp_90_100 <- fin_imp %>%
  filter(logpop > quantile(fin_seg$logpop, c(.90), na.rm = T) & logpop < quantile(fin_seg$logpop, c(1), na.rm = T))

nrow(fin_imp_90_100)
median(fin_imp_90_100$logpop)

ini <- mice(fin_imp_90_100, maxit = 0, print = FALSE)

imp_90_100 <- mice(fin_imp_90_100, method = meth, maxit = 5)

fit_imp_90_100 <- with(imp_90_100, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_90_100 <- pool(fit_imp_90_100)
imp_fs_90_100 <- summary(pool_fs_90_100)

quantile(fin_seg$logpop, c(.90), na.rm = T) & logpop < quantile(fin_seg$logpop, c(1), na.rm = T)

exp(quantile(fin_seg$logpop, c(.90), na.rm = T))
exp(quantile(fin_seg$logpop, c(.95), na.rm = T))
exp(quantile(fin_seg$logpop, c(1), na.rm = T))

```{r 25_100k}

fin_imp_25_100k <- fin_imp %>%
  filter(logpop < log(100000) & logpop > log(25000))

nrow(fin_imp_25_100k)

ini <- mice(fin_imp_25_100k, maxit = 0, print = FALSE)

imp_25_100k <- mice(fin_imp_25_100k, method = meth, maxit = 5)

fit_imp_25_100k <- with(imp_25_100k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_25_100k<- pool(fit_imp_25_100k)
imp_fs_pop_25_100k<- summary(pool_fs_25_100k)

```{r 100-250k}

fin_imp_100_250k <- fin_imp %>%
  filter(logpop > log(100000) & logpop < log(250000))

nrow(fin_imp_100_250k)

ini <- mice(fin_imp_100_250k, maxit = 0, print = FALSE)

imp_100_250k <- mice(fin_imp_100_250k, method = meth, maxit = 5)

fit_imp_100_250k <- with(imp_100_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_100_250k<- pool(fit_imp_100_250k)
imp_fs_pop_100_250k <- summary(pool_fs_100_250k)

```{r 250_500k}

fin_imp_250_500k <- fin_imp %>%
  filter(logpop < log(500000) & logpop > log(250000))

nrow(fin_imp_250_500k)

ini <- mice(fin_imp_250_500k, maxit = 0, print = FALSE)

imp_250_500k <- mice(fin_imp_250_500k, method = meth, maxit = 5)

fit_imp_250_500k <- with(imp_250_500k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_250_500k <- pool(fit_imp_250_500k)
imp_fs_pop_250_500k <- summary(pool_fs_250_500k)

@@

fit_imp_50k <- with(imp_50k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

@@

fit_imp_250k <- with(imp_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

@@

```{r 25_50k}

fin_imp_25_50k <- fin_imp %>%
  filter(logpop > log(25000) & logpop < log(50000))

nrow(fin_imp_25_50k)
median(fin_imp_25_50k$logpop)

ini <- mice(fin_imp_25_50k, maxit = 0, print = FALSE)

imp_25_50k <- mice(fin_imp_25_50k, method = meth, maxit = 5)

fit_imp_25_50k <- with(imp_25_50k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_25_50k<- pool(fit_imp_25_50k)
imp_fs_pop_25_50k<- summary(pool_fs_25_50k)

```{r 50_100k}

fin_imp_50_100k <- fin_imp %>%
  filter(logpop > log(50000) & logpop < log(100000))

nrow(fin_imp_50_100k)
median(fin_imp_50_100k$logpop)

ini <- mice(fin_imp_50_100k, maxit = 0, print = FALSE)

imp_50_100k <- mice(fin_imp_50_100k, method = meth, maxit = 5)

fit_imp_50_100k<- with(imp_50_100k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_50_100k <- pool(fit_imp_50_100k)
imp_fs_pop_50_100k <- summary(pool_fs_50_100k)

```{r 100_250k}

fin_imp_100_250k <- fin_imp %>%
  filter(logpop > log(100000) & logpop < log(250000))

nrow(fin_imp_100_250k)
median(fin_imp_100_250k$logpop)

ini <- mice(fin_imp_100_250k, maxit = 0, print = FALSE)

imp_100_250k <- mice(fin_imp_100_250k, method = meth, maxit = 5)

fit_imp_100_250k<- with(imp_100_250k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_100_250k <- pool(fit_imp_100_250k)
imp_fs_pop_100_250k <- summary(pool_fs_100_250k)

```{r 250_500K}

@@

nrow(fin_imp_250_500k)
median(fin_imp_250_500k$logpop)

@@

ini <- mice(fin_imp_250_500k, maxit = 0, print = FALSE)

imp_250_500k <- mice(fin_imp_250_500k, method = meth, maxit = 5)

fit_imp_250_500k<- with(imp_250_500k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_250_500k <- pool(fit_imp_250_500k)
imp_fs_pop_250_500k <- summary(pool_fs_250_500k)

```{r 500_1m}

fin_imp_500_1m <- fin_imp %>%
  filter(logpop > log(500000) & logpop < log(1000000))

nrow(fin_imp_500_1m)
median(fin_imp_500_1m$logpop)
# generate a blank run to get the method matrix

ini <- mice(fin_imp_500_1m, maxit = 0, print = FALSE)

imp_500_1m <- mice(fin_imp_500_1m, method = meth, maxit = 5)

fit_imp_500_1m<- with(imp_500_1m, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_500_1m <- pool(fit_imp_500_1m)
imp_fs_pop_500_1m <- summary(pool_fs_500_1m)

```{r 1m+}

fin_imp_1m <- fin_imp %>%
  filter(logpop > log(1000000))

nrow(fin_imp_1m)
median(fin_imp_1m$logpop)
# generate a blank run to get the method matrix

ini <- mice(fin_imp_1m, maxit = 0, print = FALSE)

imp_1m <- mice(fin_imp_1m, method = meth, maxit = 5)

fit_imp_1m<- with(imp_1m, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_1m <- pool(fit_imp_1m)
imp_fs_pop_1m <- summary(pool_fs_1m)

```{r 500,000+}

fin_imp_500k <- fin_imp %>%
  filter(logpop > log(500000))

nrow(fin_imp_500k)
median(fin_imp_500k$logpop)
# generate a blank run to get the method matrix

ini <- mice(fin_imp_500k, maxit = 0, print = FALSE)

imp_500k <- mice(fin_imp_500k, method = meth, maxit = 5)

fit_imp_500k <- with(imp_500k, felm(dgepercap_cpi ~ H_citytract_NHW_i + diversityinterp + pctblkpopinterp + pctasianpopinterp + pctlatinopopinterp + medinc_cpi + pctlocalgovworker_100 + pctrentersinterp + pctover65 + pctcollegegradinterp | factor(geo_id2) |0| geo_id2))

pool_fs_500k <- pool(fit_imp_500k)
imp_fs_pop_500k <- summary(pool_fs_500k)

```{r 250,000+}

fin_imp_250k <- fin_imp %>%
  filter(logpop > log(250000))

nrow(fin_imp_250k)
median(fin_imp_250k$logpop)
# generate a blank run to get the method matrix

@@

imp_250k <- mice(fin_imp_250k, method = meth, maxit = 5)

@@

pool_fs_250k <- pool(fit_imp_250k)
imp_fs_pop_250k <- summary(pool_fs_250k)

@@

imp_felm1_sum[1,2]
imp_under_baqir_1_sum
imp_over_baqir_1_sum
coef(felm1)[1]
imp_fs_pop_top_1_sum

@@

model_coeff <- tibble(
  variable = c("White/Non-White Seg. Index", "Diversity", 
               "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity", 
               "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity", 
               "White/Non-White Seg. Index", "Diversity", 
               "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity", 
               "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity",
                "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity",
                "White/Non-White Seg. Index", "Diversity",
               "White/Non-White Seg. Index", "Diversity"),
  estimate = c(imp_under_baqir_1_sum[1,2], imp_under_baqir_1_sum[2,2],
               imp_felm1_sum[1,2], imp_felm1_sum[2,2],
                imp_fs_pop_bottom_60[1,2], imp_fs_pop_bottom_60[2,2],
               imp_fs_60_80[1,2], imp_fs_60_80[2,2],
                imp_fs_80_90[1,2], imp_fs_80_90[2,2],
                imp_fs_80_100[1,2], imp_fs_80_100[2,2],
               coef(felm1)[1], coef(felm1)[2],
               imp_fs_90_100[1,2], imp_fs_90_100[2,2],
               imp_fs_pop_25_50k[1,2], imp_fs_pop_25_50k[2,2],
               imp_fs_pop_top_1_sum[1,2], imp_fs_pop_top_1_sum[2,2],
               imp_over_baqir_1_sum[1,2], imp_over_baqir_1_sum[2,2],
               imp_fs_pop_50_100k[1,2], imp_fs_pop_50_100k[2,2],
               imp_fs_pop_100_250k[1,2], imp_fs_pop_100_250k[2,2],
               imp_fs_pop_250_500k[1,2], imp_fs_pop_250_500k[2,2],
               imp_fs_pop_500_1m[1,2], imp_fs_pop_500_1m[2,2],
               imp_fs_pop_1m[1,2], imp_fs_pop_1m[2,2],
                imp_fs_pop_25_100k[1,2], imp_fs_pop_25_100k[2,2],
               imp_fs_pop_100_250k[1,2], imp_fs_pop_100_250k[2,2],
               imp_fs_pop_250_500k[1,2], imp_fs_pop_250_500k[2,2]),
  std_error = c(imp_under_baqir_1_sum[1,3], imp_under_baqir_1_sum[2,3],
                imp_felm1_sum[1,3], imp_felm1_sum[2,3],
                imp_fs_pop_bottom_60[1,3], imp_fs_pop_bottom_60[2,3],
                imp_fs_60_80[1,3], imp_fs_60_80[2,3],
                imp_fs_80_90[1,3], imp_fs_80_90[2,3],
                imp_fs_80_100[1,3], imp_fs_80_100[2,3],
                summary(felm1)$coeff[1,2], summary(felm1)$coeff[2,2],
                imp_fs_90_100[1,3], imp_fs_90_100[2,3],
                imp_fs_pop_25_50k[1,3], imp_fs_pop_25_50k[2,3],
                imp_fs_pop_top_1_sum[1,3], imp_fs_pop_top_1_sum[2,3],
                imp_over_baqir_1_sum[1,3], imp_over_baqir_1_sum[2,3],
                imp_fs_pop_50_100k[1,3], imp_fs_pop_50_100k[2,3],
                imp_fs_pop_100_250k[1,3], imp_fs_pop_100_250k[2,3],
                imp_fs_pop_250_500k[1,3], imp_fs_pop_250_500k[2,3],
                imp_fs_pop_500_1m[1,3], imp_fs_pop_500_1m[2,3],
                imp_fs_pop_1m[1,3], imp_fs_pop_1m[2,3],
                imp_fs_pop_25_100k[1,3], imp_fs_pop_25_100k[2,3],
               imp_fs_pop_100_250k[1,3], imp_fs_pop_100_250k[2,3],
               imp_fs_pop_250_500k[1,3], imp_fs_pop_250_500k[2,3]),
  model = c( "fin_imp_pop_under_baqir", "fin_imp_pop_under_baqir",
             "fin_imp", "fin_imp",
             "fin_imp_bottom_60",  "fin_imp_bottom_60", 
             "fin_imp_60_80", "fin_imp_60_80", 
             "fin_imp_80_90", "fin_imp_80_90",
             "fin_imp_80_100", "fin_imp_80_100",
            "fin_dge", "fin_dge",
            "fin_imp_90_100", "fin_imp_90_100",
            "fin_imp_25_50k", "fin_imp_25_50k",
            "fin_imp_top_1", "fin_imp_top_1",
            "fin_imp_pop_over_baqir", "fin_imp_pop_over_baqir",
            "fin_imp_50_100k", "fin_imp_50_100k",
            "fin_imp_100_250k", "fin_imp_100_250k",
            "fin_imp_250_500k", "fin_imp_250_500k",
            "fin_imp_500_1m", "fin_imp_500_1m",
            "fin_imp_1m", "fin_imp_1m",
            "fin_imp_25_100", "fin_imp_25_100",
            "fin_imp_100_250", "fin_imp_100_250",
            "fin_imp_250_500", "fin_imp_250_500")
)

@@

```{r dataset_rows_in_analysis}

complete_fs <- complete(imp_fs,1) %>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_over_baqir <- complete(imp_fs_pop_overbaqir, 1)%>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_under_baqir <- complete(imp_fs_pop_under_baqir, 1)%>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_top_1 <- complete(imp_fs_pop_top_1, 1)%>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_bottom_60 <- complete(imp_bottom_60, 1)%>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_1m <- complete(imp_1m, 1)%>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_25_50k <- complete(imp_25_50k, 1)%>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_50_100k <- complete(imp_50_100k, 1)%>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_100_250k <- complete(imp_100_250k , 1)%>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_250_500k <- complete(imp_250_500k , 1)%>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_500_1m <- complete(imp_500_1m , 1)%>%
  filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)), !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_60_80 <- complete(imp_60_80, 1) %>%
    filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)),
           !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_80_100 <- complete(imp_80_100, 1) %>%
    filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)),
           !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)

complete_80_90 <- complete(imp_80_90, 1) %>%
    filter(!(is.na(dgepercap_cpi)), !(is.na(H_citytract_NHW_i)),
           !(is.na(diversityinterp)),
         !(is.na(pctblkpopinterp)), !(is.na(pctasianpopinterp)),
         !(is.na(pctlatinopopinterp)),
         !(is.na(medinc_cpi)), !(is.na(pctlocalgovworker_100)),
         !(is.na(pctrentersinterp)),
         !(is.na(pctover65)), !(is.na(pctcollegegradinterp)),
         !(is.na(logpop)), dgepercap_cpi != 0)
